Identifying `rtrees` Training Data

### 2020-09-30 journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.Rmd
last few small changes

Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons`:

@@

Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands`:

>>>>

Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons` (Heike identified that Hamby173-Br3-B2-L1 has damage on the bullet, but she is not sure why Hamby173-BrUnk-BM-L4 was left out):

@@

Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands` (Heike confirmed that bullet E is known to have issues):
